---
title: "my-analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aa-my-analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(userpackage)
```

## List all packages needed

```{r}
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(testthat)
```


## Read and clean the dataset

This week's data is from the [NYC Squirrel Census](https://www.thesquirrelcensus.com/) - raw data at [NY Data portal](https://data.cityofnewyork.us/Environment/2018-Central-Park-Squirrel-Census-Squirrel-Data/vfnx-vebw).  

- This dataset is saved as a csv file in the project.  
- Column `date` needs to be transformed as date.  
- Column `age` needs to be cleaned up: `?` => `NA`


<!-- Add a chunk: Ctrl + Alt + I -->
```{r}
# data cleaning could be in "data-raw"
path <- system.file("example-data/nyc_squirrels.csv", package = "userpackage")
nyc_squirrels <- read_csv(path) %>% 
  mutate(
    date = mdy(date),
    age = if_else(age == "?", NA_character_, age)
  )

glimpse(nyc_squirrels)
```

## Filter, count and plot

- Parameter to choose age group to be kept for analysis
- Filter on age group
- Count number of individual according to fur color

```{r}
# Data analysis
squirrels_filtered <- filter_count(x = nyc_squirrels, my_age = "Adult")
```

- Plot counts according to fur color
    + Create title according to age chosen

```{r}
# Data analysis
filter_count(x = nyc_squirrels, my_age = "Adult") %>% 
  plot_count(my_age = "Adult")
```

> Separately analyse juveniles and adults
