---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# userpackage

<!-- badges: start -->
<!-- badges: end -->
<!-- description: start -->
This is package {userpackage}: Analyse NYC Squirrel Dataset.  
The aim of {userpackage} is to propose an example package built with "Rmd first" method during conferences and tutorials.
Current version is 0.0.0.9000.
<!-- description: end -->

## Installation
<!-- install: start -->
The list of dependencies required to install this package is: dplyr, ggplot2, knitr, lubridate, magrittr, readr, rmarkdown, testthat.

To install the package, you can run the following script

```{r, echo=TRUE, eval=FALSE}
# install.packages("remotes")
remotes::install_local(path = "userpackage.0.0.0.9000.tar.gz")
```

In case something went wrong, you may want to install dependencies before using:

```{r, echo=TRUE, eval=FALSE}
# No Remotes ----
# Attachments ----
to_install <- c("dplyr", "ggplot2", "magrittr")
  for (i in to_install) {
    message(paste("looking for ", i))
    if (!requireNamespace(i)) {
      message(paste("     installing", i))
      install.packages(i)
    }
  }
```

<!-- install: end -->

## Reminder of the workflow

1. **Directly create a new "R package using devtools"**  
    + `usethis::create_package("my.project")` if forgotten
1. Create "dev_history.R" at the root
    + Use it to store all your `usethis::` and co...
1. Fill in DESCRIPTION file
1. Create a small dataset (reprex)
    + Store in "inst/example-data" (or in "data")
1. "Rmd first": Create a vignette
    + `usethis::use_vignette("aa-exploration")`
1. **Build your functions along with vignette**
    + Document parameters
    + Add example of use
    + Store in "R/" (`usethis_use_r()`)
    + Run `attachment::att_amend_desc()`
    + Add unit tests
1. Check your package regularly (`devtools::check()`)
1. Use git and continuous integration
1. Show your work to your colleagues and customers (`pkgdown::build_site()`)

