---
title: "Squirrels"
author: "Sébastien Rochette"
date: "02/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE
)
```

## List all packages needed

```{r}
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
```


## Read and clean the dataset

This week's data is from the [NYC Squirrel Census](https://www.thesquirrelcensus.com/) - raw data at [NY Data portal](https://data.cityofnewyork.us/Environment/2018-Central-Park-Squirrel-Census-Squirrel-Data/vfnx-vebw).  

- This dataset is saved as a csv file in the project.  
- Column `date` needs to be transformed as date.  
- Column `age` needs to be cleaned up: `?` => `NA`


<!-- Add a chunk: Ctrl + Alt + I -->
```{r}
# data cleaning could be in "data-raw"
nyc_squirrels <- read_csv("data-raw/nyc_squirrels.csv") %>% 
  mutate(
    date = mdy(date),
    age = if_else(age == "?", NA_character_, age)
  )

glimpse(nyc_squirrels)
```

## Filter, count and plot

- Parameter to choose age group to be kept for analysis
- Filter on age group
- Count number of individual according to fur color
- Plot counts according to fur color
    + Create title according to age chosen

```{r}
my_age <- c("Adult", "Juvenile")[1]

squirrels_filtered <- nyc_squirrels %>% 
  filter(age %in% my_age) %>% 
  count(primary_fur_color)

ggplot(squirrels_filtered) +
  aes(x = primary_fur_color, y = n, fill = primary_fur_color) +
  geom_col() +
  scale_fill_manual(
    values = c("Cinnamon" = "#D2691E",
               "Black" = "black",
               "Gray" = "gray40"),
    na.value = "cyan4") +
  labs(
    title = paste("Count of", tolower(my_age), "squirrels by fur color"),
    x = "Primary fur color",
    y = "Count"
  ) + 
  guides(fill = FALSE) +
  theme_classic()
```

> Separately analyse juveniles and adults
