---
title: "Squirrels"
author: "Sébastien Rochette"
date: "02/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## List all packages needed

```{r}
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
```


## Read and clean the dataset

This week's data is from the [NYC Squirrel Census](https://www.thesquirrelcensus.com/) - raw data at [NY Data portal](https://data.cityofnewyork.us/Environment/2018-Central-Park-Squirrel-Census-Squirrel-Data/vfnx-vebw).  

- This dataset is saved as a csv file in the project.  
- Column `date` needs to be transformed as date.  
- Column `age` needs to be cleaned up: `?` => `NA`


<!-- Add a chunk: Ctrl + Alt + I -->
```{r}
# data cleaning could be in "data-raw"
nyc_squirrels <- read_csv("data-raw/nyc_squirrels.csv") %>% 
  mutate(
    date = mdy(date),
    age = if_else(age == "?", NA_character_, age)
  )

glimpse(nyc_squirrels)
```

## Filter, count and plot

- Parameter to choose age group to be kept for analysis
- Filter on age group
- Count number of individual according to fur color

```{r}
# Function
filter_count <- function(x, my_age) {
  # Test
  if (!all(c("age", "primary_fur_color") %in% names(x))) {
    stop("x should contain 'age' and 'primary_fur_color' columns")
  }
  x %>% 
    filter(age %in% my_age) %>% 
    count(primary_fur_color)
}
# Example
squirrels_filtered <- filter_count(x = nyc_squirrels, my_age = "Adult")
```

- Plot counts according to fur color
    + Create title according to age chosen

```{r}
# Function
plot_count <- function(x, my_age = "all") {
  # Test
  if (!all(c("n", "primary_fur_color") %in% names(x))) {
    stop("x should contain 'n' and 'primary_fur_color' columns")
  }
  ggplot(x) +
    aes(x = primary_fur_color, y = n, fill = primary_fur_color) +
    geom_col() +
    scale_fill_manual(
      values = c("Cinnamon" = "#D2691E",
                 "Black" = "black",
                 "Gray" = "gray40"),
      na.value = "cyan4") +
    labs(
      title = paste("Count of", tolower(my_age), "squirrels by fur color"),
      x = "Primary fur color",
      y = "Count"
    ) + 
    guides(fill = FALSE) +
    theme_classic()
}
# Example
filter_count(x = nyc_squirrels, my_age = "Adult") %>% 
  plot_filtered(my_age = "Adult")
```

> Separately analyse juveniles and adults
